---
title: "Ilze risk indicators"
output:
  html_document:
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
    code_folding: hide
  pdf_document:
    toc: yes
---

```{r}
knitr::opts_chunk$set(
  fig.width = 12,
  fig.height = 8,
  fig.path = 'Figs/',
  echo = FALSE,
  include= TRUE,  # for the chunks to be displayed
  warning = FALSE,
  message = FALSE,
  out.width = "75%"
)# Use include=TRUE for the chunks to be displayed
```

Packages

```{r}
pacman::p_load(tidyverse, 
               visdat, # for NAs
               table1, 
               expss, # to change labels
               janitor,  # for data cleaning
               sjPlot,   # for model visualization
               gtsummary, # for summary tables
               performance # for regression diagnostic check
)
```

Dataset

```{r}
ecc <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRaanB0FUyB-NrIJpC_OpxZ2E6h3gsZ5sM65E-5PEvXxew2UGfBWXAU38jGww_GklQCDWyDJ63o-KNc/pub?gid=0&single=true&output=csv")
```

```{r}
ecc <- ecc %>% 
  janitor::clean_names() %>% 
  janitor::remove_empty(which = c("rows", "cols")) %>% 
  select(-c(code, 
            syrup, 
            examination_date, 
            birth_date))
```

```{r}
visdat::vis_dat(ecc)
```

Change output variable

```{r}
ecc <- ecc %>% 
  mutate(ecc2 = case_when(
    ecc == "Yes" ~ "1", 
    TRUE ~ "0"
  )) %>% 
  mutate(ecc2 = as.integer(ecc2)) 
```



## Combine some variables

```{r}
ecc <- ecc %>% 
  mutate(hygiene_combined_foranalysis = fct_collapse(hygiene_combined_foranalysis, 
              "Twice daily and more low fluoride" = c("Twice daily and more Fluoride Recently", "Twice daily and more Fluoride Free") , 
              "At least once per day F" = c("In evenings Fluoride Always", "Twice daily and more Fluoride Always")))
```



# EDA

```{r}
ecc %>% 
  janitor::tabyl(ecc2)
```

```{r}
table(ecc$ecc2)
```

## age

```{r}
ecc %>% 
  summarize(mean(age), sd(age))
```


```{r}
ecc %>% 
  ggplot(aes(x = age)) +
  geom_histogram(bins = 5) +
  facet_grid(gender ~ .)
```

## age by ecc


```{r}
ecc %>% 
  ggplot(aes(x = age)) +
  geom_histogram(bins = 5) +
  facet_grid(ecc ~ .)
```


Mark baseline factors

```{r}
ecc <- ecc %>% 
  mutate(toothbrushing_frequency = fct_relevel(toothbrushing_frequency, "Twice daily and more" ))
```

toothbrushing_frequency = Twice daily and more

```{r}
ecc <- ecc %>% 
  mutate(dental_hygienist_attendance = fct_relevel(dental_hygienist_attendance, "Regular twice year", ">2", "1", "0")) %>% 
  mutate(dentist_attendance = fct_relevel(dentist_attendance, "Regular twice year", ">2", "1", "0")) %>% 
  mutate(breastfeeding_code = fct_relevel(breastfeeding_code, "<6", ">6", ">12", ">24")) %>% 
  mutate(toothpaste = fct_relevel(toothpaste, "Fluoride", "Low Fluoride", "Fluoride Free"))
```

```{r}
ecc <- ecc %>%
  mutate(general_health_01 = as.character(general_health_01))
```

```{r}
# ecc <- ecc %>% 
#  mutate(breastfeedong = case_when(
#    breastfeedong == "baro" ~ "24", 
#    TRUE ~ breastfeedong
#  )) %>% 
#  mutate(breastfeedong = as.double(breastfeedong))
```

#Table 1

```{r}
table1::table1(
  ~ age + gender + parental_brushing + toothbrushing_frequency + toothpaste + hygiene_combined_foranalysis + sugar_liquid + sugar_solid + imrovement_diet + diet_combined_foranalysis + plaque + bottle_feeding + breastfeeding_code + mouth_breathing |
  ecc,
  data = ecc
  )
```
## Table 1 gtsummary (sergio)

### Modify labels

```{r}
# the labels to change

ecc <- expss::apply_labels(
  ecc,
  "age" = "Age",
  "gender" = "Gender ",
  "parental_brushing" = "Parents brush teeth ",
  "toothbrushing_frequency" = "Tooth brushing frecuency",
  "toothpaste" = "F Toothpaste use",
  "hygiene_combined_foranalysis" = "Toothbrushing (Frequency and F) ",
  "sugar_liquid" = "Consumes sugary liquids",
  "sugar_solid" = "Consumes sugary solids",
  "imrovement_diet" = "Change in the last 12 months towards healthy dietary habits ",
  "diet_combined_foranalysis" = "Dietary habits ",
  "plaque" = "Plaque presence",
  "bottle_feeding" = "Bottle feeding ",
  "breastfeeding_code" = "Breastfeeding ",
  "mouth_breathing" = "Mouth breathing"
)
```


## REMOVE ALL CHILDREN > 6 YEARS OLD

```{r}
ecc <- ecc %>% 
  filter(age < 6)
```




### The table one with gtsummary
```{r}
ecc %>%

  mutate(ecc = fct_recode(ecc, "Caries free" = "No",
                          "ECC" = "Yes")) %>%
  select(
    age ,
    gender ,
    parental_brushing ,
    toothbrushing_frequency ,
    toothpaste ,
    hygiene_combined_foranalysis ,
    sugar_liquid ,
    sugar_solid ,
    imrovement_diet ,
    diet_combined_foranalysis ,
    plaque ,
    bottle_feeding ,
    breastfeeding_code ,
    mouth_breathing,
    ecc
  ) %>%
  gtsummary::tbl_summary(
    by = ecc,
    label = age ~ "Age"
  ) %>%
  gtsummary::bold_labels() %>%
  gtsummary::add_overall() 
```



# Regression model

delete the never in toothbrushing frequency

```{r}
# ecc$toothbrushing_frequency <-  fct_collapse(ecc$toothbrushing_frequency, "In mornings or less than once" # = c("In mornings or less than once", "Never"))
```

Omit NA in breastfeeding code

```{r}
ecc <- ecc %>% 
  filter(!is.na(breastfeeding_code)) %>% 
  filter(breastfeeding_code != "#N/A") 
```


Drop levels

```{r}

ecc$breastfeeding_code <- fct_drop(ecc$breastfeeding_code)
```


# Table 1a

```{r}
ecc %>%
  select(
    gender ,
    age ,
    ecc2 ,
    general_health_01 ,
    parental_brushing ,
    dental_hygienist_attendance ,
    dentist_attendance ,
    toothbrushing_frequency ,
    toothpaste ,
    
    improvement_hygiene ,
    sugar_liquid ,
    sugar_solid ,
    
    # imrovement_diet ,
    plaque ,
    bottle_feeding ,
    # breastfeedong +
    breastfeeding_code ,
    mouth_breathing
  ) %>%
  gtsummary::tbl_summary(by = gender) %>%
  gtsummary::add_overall() %>% 
  gtsummary::bold_labels()
```


# Regression table
## m1 full

relevel for analysis

```{r}

ecc <- ecc %>%
  mutate(
    hygiene_combined_foranalysis = fct_relevel(
      hygiene_combined_foranalysis,
      "At least once per day F",
      "Twice daily and more low fluoride",
      "In evenings Fluoride Recently", 
      "In evenings Low Fluoride", 
      "Less than once per day and/or no fluoride"
    )
  ) 


```

Hygienist

```{r}
ecc <- ecc %>% 
  mutate(dental_hygienist_attendance = fct_collapse(dental_hygienist_attendance,
                                                    "Regular" =  c("Regular twice year", ">2")))
```



```{r}
m1 <-
  glm(
    ecc2 ~
      age +
      gender +
      
      hygiene_combined_foranalysis +
      
      parental_brushing +
      plaque +
      
      dental_hygienist_attendance +
      
      bottle_feeding +
      breastfeeding_code +
      
      diet_combined_foranalysis +
      mouth_breathing,
    data = ecc,
    family = binomial
  )
```

```{r}
gtsummary::tbl_regression(m1, exponentiate = TRUE) %>% 
  gtsummary::bold_labels() %>% 
  gtsummary::add_n(location = "level")
```


```{r}
sjPlot::plot_model(m1) +
  theme_light() + 
  labs(title = "Regression model for ECC indicators") +
  geom_hline(yintercept = 1, linetype="dotted")
  
```





## Check model

### m1

```{r}
performance::check_model(m1)
```
```{r}
report::report_text(m1)
```



